---
title: "Figures_to_Journal_Specifications"
output:
  pdf_document: default
  html_document: default
---

You've made a great graph, or you have some exciting data, and you want to create a clear, informative graph, that is accessible to everyone and is up to the specifications of the journal you are submitting to. 

Porzana Solutions can help. 

I can ensure that your figure is accessible to those with colorblindness, or the legally blind. 

I can write screen reader captions for your figures so that those who use screen readers can still use and understand your figures. 

I do most of my graphing in ggplot2, and with this R package can make a figure to your exact specifications. 


```{r, message=FALSE, warning=FALSE}

library(ggplot2)
library(gridExtra)
library(auriel)
library(raildata)
library(chron)
library(cowplot)
library(ResourceSelection)
library(tidyverse)
library(raildata)
library(RColorBrewer)
```

```{r, fig.height=8, fig.width=8}
states <- c("missouri","illinois","ohio","indiana","kentucky")

####
# Missouri Surveys
####

data(allbirds)

allbirds <- allbirds %>%
                mutate(species=ifelse(species=="y"|species=="yera",
                                      "Yellow Rail",species),
                       species=ifelse(species=="v"|species=="vira",
                                      "Virginia Rail",species)) %>%
                filter(species=="Yellow Rail"|species=="Virginia Rail") %>%
                mutate(state="missouri",
                       source="This Study") %>%
                select(species, state, month, day, year, source, odate)

#####
## Building Strikes
####

nonebird <- read.csv("./data/no_ebird.csv", 
                     stringsAsFactors = FALSE) %>%
              mutate(spp=ifelse(spp=="yera","Yellow Rail",spp),
                     spp=ifelse(spp=="vira","Virginia Rail",spp),
                     source=ifelse(source=="birdstrikes",
                                   "Building Strikes",source)) %>%
              filter(spp!="sora",
                     !is.na(spp),
                     state %in% states,
                     state !="illinois",
                     year>=1960,
                     month>=8&month<=11)


####
## Bluebird
####

bluebird <- read.csv("./data/the_bluebird.csv", 
                        stringsAsFactors = FALSE) %>%
                  mutate(state="missouri",
                         source="The Bluebird") %>%
                  filter(!is.na(day))

bluebird[bluebird$month=="august",]$month <- 8
bluebird[bluebird$month=="june",]$month <- 6
bluebird[bluebird$month=="december",]$month <- 12
bluebird[bluebird$month=="August",]$month <- 8
bluebird[bluebird$month=="May",]$month <- 5
bluebird[bluebird$month=="september",]$month <- 9
bluebird[bluebird$month=="october",]$month <- 10
bluebird[bluebird$month=="april",]$month <- 4
bluebird[bluebird$month=="march",]$month <- 3
bluebird[bluebird$month=="july",]$month <- 7
bluebird[bluebird$month=="november",]$month <- 11
bluebird[bluebird$month=="may",]$month <- 5

bluebird$odate <- ordinal_date_con(bluebird[,c("month","day","year")])

bbird <- bluebird %>% 
  mutate(species = ifelse(species=="year"|species=="yera",
                          "Yellow Rail",species),
         species = ifelse(species=="vira","Virginia Rail",species),
         month = as.numeric(month)) %>%
  filter(species=="Virginia Rail"|species=="Yellow Rail", 
         month>=8&month<=11) %>% 
  select(species, state, month, day, year, source, odate)

####
# eBird
####

vira <- c("Virginia Rail","vira")
yera <- c("Yellow Rail", "yera","year")
sora <- c("Sora","sora")

dat <- read.csv("./data/ebird.csv", stringsAsFactors = FALSE) %>%
          mutate(source="eBird",
                 species = ifelse(species %in% vira, 
                                  "Virginia Rail", species),
                 species = ifelse(species %in% yera, 
                                  "Yellow Rail", species)) %>%
          filter(species=="Virginia Rail"|species=="Yellow Rail",
                 year>=2000,
                 latitude<=40.5&latitude>36.5&state %in% states,
                 month>=8&month<=11) %>%
          select(species, state, month, day, year, source, odate)

###
# bring everything together
###

colnames(allbirds) <- colnames(nonebird)
colnames(bbird) <- colnames(nonebird)
colnames(dat) <- colnames(nonebird)

alldat <- bind_rows(dat,nonebird, allbirds, bbird) %>%
          filter(source!="vertnet",
                 odate>=213) %>%
          mutate(date=paste0(month,"/",day,"/",year),
                 date=as.Date(date, format="%m/%d/%y")) %>%
          filter(day>=1) %>% 
          select(spp, source, odate)


all_together_now <- alldat %>% 
                        filter(source!="This Study") %>%
                        mutate(source="Opportunistic") %>%
                        bind_rows(alldat)

summary_for_graph <- all_together_now %>%
                          group_by(source, spp) %>% 
                          summarize_each(funs(min=min(odate),
                                              q1=quantile(odate, probs=0.25),
                                              median=median(odate),
                                              q3=quantile(odate,probs=0.75), 
                                              max=max(odate)))


#####
# BNA
#####

BNA <- data.frame(source="Birds Of \nNorth America", 
                  spp=c("Virginia Rail","Yellow Rail"),
                  min=c(227,232) ,
                  q1=c(258,244) , 
                  median=c(258,244) , 
                  q3=c(283,293) , 
                  max=c(293,314))


dt <- bind_rows(summary_for_graph, BNA)

fin_dat <- dt %>%
          mutate(col=NA,
                 col = ifelse(spp=="Virginia Rail","V","Y")) %>%
          mutate(col = ifelse(source=="Birds Of North America","BNA",col)) %>%
          filter(source!="eBird"&source!="The Bluebird"&source!="Building Strikes")


vira <- all_together_now %>%
            filter(source=="This Study"|source=="Opportunistic",
                   spp=="Virginia Rail") %>%
            mutate(source=factor(source, 
                                 levels=c("This Study","Opportunistic"))) %>%
            ggplot(aes(x=odate, fill=source))+
                geom_density(alpha=0.5)+
                theme_krementz()+
                theme(legend.position="none",
                      legend.direction="vertical",
                      legend.title=element_blank(),
                      axis.text.x=element_blank(),
                      axis.title.x=element_blank(),
                      axis.ticks = element_blank(),
                      axis.title.y=element_blank())+
                ylab("Relative Density")+
                scale_fill_manual(values=c("grey",NA))+
            ggtitle("Virginia Rail")+
            xlim(214, 335)


vira_bna <- fin_dat %>%
  filter(spp=="Virginia Rail",
         source=="Birds Of \nNorth America") %>%
  ggplot()+
  geom_boxplot(
    aes(ymax=max, lower=q1, middle=median, upper=q3,
        ymin=min, x=source, fill=spp), 
        color='black', stat="identity", fill="black")+
  coord_flip()+
  theme_krementz()+
  scale_y_continuous(label = function(y) 
    strftime(chron(y, origin = c(month = 1, day = 1, year = 2016)), 
             "%b %d"), 
          breaks=c(214, 228,245,259,275,289,306,320,335,350,365), 
          limits=c(214, 335))+
  theme(axis.title.y=element_blank(),
        legend.position="none",
        axis.text.x=element_text(ang=90),
        axis.text.y=element_blank(),
        axis.ticks = element_blank())


##########################

yera <- all_together_now %>%
  filter(source=="This Study"|source=="Opportunistic",
         spp=="Yellow Rail") %>%
  mutate(source=factor(source, levels=c("This Study","Opportunistic"))) %>%
  ggplot(aes(x=odate, fill=source))+
  geom_density(alpha=0.5)+theme_krementz()+
  theme(axis.text.x=element_blank(),
        axis.title.x=element_blank(),
        legend.position=c(0.75,0.85),
        legend.title=element_blank(),
        legend.direction="vertical",
        axis.ticks = element_blank(),
        axis.title.y=element_text(size=15))+
  scale_fill_manual(values=c("grey",NA))+
  ylab("Proportion of Total Inidividuals Counted")+
  ggtitle("Yellow Rail")+
  xlim(214, 335)

yera_bna <-fin_dat %>%
          filter(spp=="Yellow Rail",
                 source=="Birds Of \nNorth America") %>%
  ggplot()+
  geom_boxplot(
    aes(ymax=max, lower=q1, middle=median, upper=q3,
        ymin=min, x=source, fill=spp), 
    color='black', stat="identity", fill="black")+
  coord_flip()+
  theme_krementz()+
  theme(axis.title.y=element_blank(),
        legend.position="none",
        axis.text.x=element_text(ang=90),
        axis.text.y=element_text(ang=90, hjust=0.5, size=12),
        axis.ticks = element_blank())+
  scale_y_continuous(label = function(y) 
    strftime(chron(y, origin = c(month = 1, day = 1, year = 2016)), 
             "%b %d"), 
              breaks=c(214, 228,245,259,275,289,306,320,335), 
              limits=c(214, 335))


# jpeg(file=paste0(Sys.Date(),"figure_III.jpeg"), height=15, width=15, units="cm", res=600)
plot_grid(yera, vira, yera_bna, vira_bna, ncol=2, align="v", rel_heights = c(3,1), rel_widths = c(1,1))
# dev.off()


write.csv(all_together_now, file="./master_figure_III.csv", row.names = FALSE)

```

